Alleviating the Topology Mismatch Problem in Distributed Overlay Networks: A Survey

### 2015-09-13 structured.tex
2015.09.20 (Vassilis) Added acknowledgements section. Updated metric definitions. Introduced timeline figures to capture termoral and trending dimensions of surveyed material. Minor fixes and typos.

\emph{Global Soft-State} \cite{XTZ2003} builds a global view to help nodes
choose shorter routing paths. To generate the proximity information, it 
combines the landmark binning method with small
scale distance probes to reveal the properties 
of the underlying network. 
%Figure \ref{fig:global_softstate} presents the landmark
%space and the mapping of the position of the nodes.

@@

\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline

@@

\emph{Mithos}~\cite{WR2003} ensures that neighboring nodes in the overlay are
close also in terms of the underlying layer by integrating proximity layout
and proximity routing overlay optimizations.

@@

A noted Mithos limitation is that the protocol cannot effectively
handle dynamic arrivals and departures from the network~\cite{RGJZ2004}. 
\cite{CCRK2004}~points out extensive probing for Mithos to determine 
distances and less accurate proximity results compared to other
virtual coordinate systems. The last issue  has been also attributed
by~\cite{WSS2005} to the iterative neighbor selection process that is 
reportedly prone to premature termination at local minima.
%%
\cite{cox_vivaldi_2004} argues that elements of the protocol's
synthetic ID generation require a centralized implementation 
affecting Mithos' scalability.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In regard to the three criteria, \emph{Mithos} stands as follows:
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% It has very good results in reducing communication latency among peers but its
% efficiency is being constrained by the fact that the proximity is calculated
% at bootstrap, assigning virtual coordinates that are used throughout of a
% nodes life cycle and thus the overlay is not adapting to a high-churn
% environment.
medium &
% Incremental probing is applied in quadrants and in two-hop distance at each
% step that does not generate a lot o control overhead.
medium &
% It is constrained by the fact that the protocol does not respond to dynamic
% peer arrivals and departures
low
\end{tabular}
}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{LAPTOP}
%
%%AD what is the nature of the "structure" overlay here???
%% VM the structure is that it is organized as a tree hierarchy.
\emph{LAPTOP} \cite{WLH2007} organizes the overlay 
into a tree-based hierarchy so that 
hops required during message routing are reduced and 
maintenance overhead is minimized.
A caching scheme is also used 
to further reduce routing table update costs. 
It is theoretically shown that 
\emph{LAPTOP} routing path length is bounded by $O(log_d(N))$ and node
joining and leaving in the overlay network is bounded by
$O(d*log_d(N))$ hops in a balanced overlay tree with $N$ representing the
number of nodes and $d$ the maximum degree of each node (i.e., number of links). 
\emph{LAPTOP} adopts the geographical layout approach  
and constructs its layout in a self-organizing and 
efficient fashion. 
The physical distances are estimated
with round-trip times to a few existing nodes in the overlay network.
%%
Each node is assigned a dot-formatted address (e.g., 1.3.4) with
each octet ranging from $1$ to $d$.
The assignment process is done by appending a unique octet 
to the address of the parent of each node, while
the root node is assigned address $1$.

@@

\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline

@@

To optimize the underlying network use,
\cite{KLKP2008} introduces proximity
controls over the \emph{vanilla Kademlia}~\cite{maymounkov_kademlia_2002} 
protocol's random \emph{ID} assignment.
% The work in this paper
% can also be considered as a more generic study of incorporating proximity into
% iterative lookup algorithms.
In its quest to improve routing performance, the overlay uses 
a cost ``yardstick'' (i.e., metric) provided by the underlying network.
% The overlay tier improves its routing performance using a cost--metric that is
% provided by the underlying tier. 
Such cost information can be acquired by:
\begin{inparaenum}[\itshape i\upshape)]
  \item measuring previous lookups,
  \item exchanging or jointly-computing measurements with others, or 
  \item using a local database to look--up information.
\end{inparaenum}

@@

\emph{Kademlia} proximity injection improves 
locality of connections among peers.
To enhance traffic locality, the use of 
{\sl MaxMind GeoIP} database\footnote{\url{http://www.maxmind.com}} 
is suggested to form clusters of nearby peers.
To this end, Vivaldi coordinates~\cite{cox_vivaldi_2004} could be 
also used as an alternative for morphing locality. 
\cite{KLKP2008} however suggests that the clustering approach 
when combined with \emph{PRS}/\emph{PNS} helps contain 
$40\%$ of messages within an \emph{ISP} and allows only $6\%$ 
to go through the backbone.
The behavior of \cite{KLKP2008} with respect to the stated criteria is deemed as follows:
%%
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Uses static information to cluster nodes which is not the most efficient
% approach in dynamic systems
% PNS reduces lookup latencies by 66\% compared to POK
medium &
% 
medium &
% MaxMind is commercial and cannot be used by FOSS P2P systems. Trying to
% expose information from P2P client can result in security issues.
medium
\end{tabular}
}
\end{center}

@@

\emph{CHOP6} \cite{MT2007} is a Chord-variant DHT that exploits
{\sl IPv6} address format as well as available \emph{RTT} information to 
enable proximity estimation among peers during message routing.
%%
Similar to \emph{Chord}~\cite{stoica_chord_2001}, 
\emph{CHOP6} uses a finger table with each entry now holding $k$$>$$1$ candidate
nodes. 
The next hop for a message is selected to be the one closest to the
destination among those $k$ candidate peers. 
This proximity is determined either
by exploiting RTT measurements or, if there is no such information yet 
(i.e., a new peer appears), by
estimating the distance in the overlay's ID space.

When joining the network, each node
receives a $64$-bit \emph{ID}. 
It comprises of a random part and the IPv6 prefix which 
is obtained by hashing the node's IP address and port
number; this combination is deployed in an effort  
to preserve the uniformity of node assignment. 
The prefix in question is based on IPv6's global routing prefix.
As IANA\footnote{\url{http://www.iana.org/}}  
assigns address blocks to regions (RIRs) which are further
distributed at national level (NIRs), the first $32$-bits of the address
can estimate the region or the country in which the node is connected. 
Thus, CHOP6's IPv6 prefix ID is used for proximity estimation
if no RTT information is available during routing. 
%%
%
%\paragraph{}
% There are three cases in which a node chooses the next hop according to
% information it possesses.
%\begin{itemize}
% \item When no information about RTT is available candidate next hops, the
%  sender just selects a node in the finger table entry which shares the longest
% prefix with the destination.
% \item There is another possibility that after some communication with other
%  nodes, the source node should know of the RTTs to some of the nodes in finger
% table entry. In this case, the source node chooses the one with the smallest
% RTT with probability $p$. If there is a node with no measured RTT then the
% sender can select such a node with probability $1 - p$
% \item In this last case the source node has already communicated with all
%  candidate node in the finger table entry. Thus, the node selects the node
% whose RTT is the smallest with probability $p$, the one with the second
% smallest with probability $q$ and so on, where $0 \leq \ldots < r < q < p < 1$
% and $p+q+r+\ldots \leq 1$
%\end{itemize}
%
With respect to the three qualitative criteria, \emph{CHOP6} stands as follows:
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Simple approach that exploits proximity but it is coarse grained and thus not
% efficient.
low &
% Its static nature imposes low overhead to the network
low &
% IPv6 is still not widely applied and supported.
medium
\end{tabular}
}
\end{center}

@@

%%AD a better connection with the mismatch problem has to be made... 
%%		.. in the form of 1-2 lines (or short statements). 
%%
%% VM Added some extra lines and restructured the text
\emph{T2MC}'s~\cite{SLCGZ2008} objective is to diminish the redundant multiple
messages that may unnecessarily cross autonomous system (\emph{AS}) boundaries.
Inter-\emph{AS} links are the costliest to ISPs and hence, 
minimizing topology mismatches greatly affects pertinent operational expenditure.
%%
To achieve this, each node exploits the stable structure of
the Internet routers to help solve a clustering problem. 
The algorithm uses {\sl traceroute}-logs to detect inter-\emph{AS} boundaries 
and clusters peers to either nearby or 
far-away groups by applying a customized $k$-mean classification ($k=2$).
%%
When joining the network, the peer randomly picks an IP and uses
traceroute and selects the routers with
minimum and maximum latencies in the above {\sl traceroute} path 
as initial centroids for the ``nearby'' and ``far-away'' sets respectively.
Following an iterative procedure, the node comes up with the two sets 
demonstrating minimum intra-set latency variance.
At this stage, routers in the ``far-away'' set are not considered critical.
%%
%%AD skipping the details???? JUST CHECK
% Skipping the details of the algorithm, it picks the routers with
% minimum and maximum latencies in the above traceroute path as initial centroids
% for the ``near'' and ``remote'' sets respectively and after some iterations it
% ends up with two sets having the minimum intra-set latency variance. 
%%
% The router from the ``far-away'' set that presents the closest distance 
% from the peer in terms of hops, is designated as beacon.
% Any node portraying distance longer that the above is classified 
% as 
% 
% to the peer, in terms of hops, is designated as a beacon.
% Any node whose distance is measured to be longer that the distance 
% between 
% 
% The router with the minimum hops in the ``remote'' set is set up as the hop
% threshold and anything above that is classified as the ``remote'' router cluster
% for that peer. 
% Similarly, 
In contrast, the router from the ``near'' set
having the maximum number of hops 
from the just-joining peer is key as it denotes an edge--gateway. 
Peers that share the same edge--gateway or other members in the ``nearby'' 
router cluster are considered intra-\emph{AS} neighbors.
%%AD the final phrase for this is missing! So what??? What is achieved? 1 sentence.

Even though {\sl traceroute}
provides detailed information about the network structure, 
its extensive use may create overhead on the overall network structure. 
Administrators thus frequently
disable {\sl traceroute} support on their routers and this 
undoubtly affects \emph{T2MC}'s operation.
%%
Although overall experimental results have been encouraging, 
\emph{T2MC} is considered rather coarse-grained as it only
classifies neighbors into two groups \cite{QLZG2009}.
%
%T2MC \cite{SLCGZ2008} uses trace-route logs to detect different autonomous
%systems and cluster close by peers, thus reducing redundant traffic that crosses
%autonomous system boundaries. T2MC uses a customized k-mean classification
%algorithm with $k=2$ to perform the classification, and exploits the stable
%structure of the Internet routers to guide clustering. The peer chooses the
%minimum and maximum Latency results from the trace-route to initialize the
%centroids of two sets. Then the peer calculates, for all hops along its
%trace-routed path, the peer calculates the absolute distance to these centroids
%of both sets and assigns the routers to that centroid with which it has the
%smaller absolute distance. After that, the mean and variance values are
%calculated and if the variance is larger than a predefined threshold then the
%algorithm sets the two latency mean values as new centroids for the two sets and
%loops again. Ultimately peer will end up with two sets having the minimum
%intra-set variance. The peer, then, chooses the router from the second set with
%the minimum hops attribute and sets it as a threshold. The selected router and
%all others whose hops attribute is larger than the threshold are classified as
%\emph{remote} router cluster. The remaining are classified as \emph{near}. From
%the near class, the peer chooses the one with maximum hops attribute as its edge
%router, and registers it along with all near clusters into the DHT of the
%\p\ overlay. As new peers join the network, those that share the same edge
%router or any of the members of the near router clusters, would form a close
%peer cluster. As Edge routers can provide more valuable information than other
%members of the near set, T2MC was designed to prioritize interaction of peers
%and edge gateways.
%
%
% TODO: SOME DISCUSSION
%
%The use of Trace-route as a tool for implementing the distance measuring
%infrastructure raise concerns about its efficiency and scalability. Being,
%primarily, a network diagnostic utility,
% Even though trace-route provides detailed information about the network
% structure, its excessive use creates additional overhead that stresses further
% the overall network infrastructure. This forces network administrators to
% disable its support from the routers they manage, thus jeopardizing the
% effectiveness of the T2MC algorithm.
%
\emph{T2MC} fares as follows:
%%
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% The efficiency of choosing close by peers is very good and reported almost
% 65\% better than that of GNP (and thus generally of static landmarking as a
% whole)
high &
% trace-route is a very heavy tool and thus incurs excessive burden to the
% network resources.
high &
% Trace-route is categorized as too heavy-weighted and intrusive for use in a
% larger scale system \cite{RKHS2002}. Additionally, disabling
% ICMP is a common administrative policy for edge sites to enforce security,
% while dumping BGP routing tables\cite{krishnamurthy_bgpclust_2000} is not
% directly available to the application layer.
low
\end{tabular}
}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{PChord}
\emph{PChord} \cite{HLYW2005} is based on the \emph{Chord DHT} and incorporates
proximity in its routing mechanism. 
To achieve this, the standard finger table
is augmented with a \emph{proximity list} that contains
nodes in the network found nearby in terms of RTT.
%in this way, the next hop can be decided based on both progress
%towards the key and the physical proximity of the candidate nodes.
%%AD
%% I am not sure about the "best progress" term - what does it really mean???
%% VM changed the above slightly to address the above comment. Generally
%% in DHTs when a node receives a search query for a key that it does not have
%% the data for, it routes the request to that node in its routing table that
%% is closest to the key. That is what I mean with best progress to the keys
%% In topology aware systems and topology aware routing we have the requirement
%% that the next hop should be the closest one which in many cases can be
%% a competing requirement with the best progress to the key requirement I
%% just described. 
In this respect, the next hop during routing can be decided based on both the
direction towards the search key and minimizing the cost of that hop.

@@

Unfortunately the overlay maintenance cost is somewhat higher than
\emph{Chord} as additional heart-beat messages are required for
connection verification for the entries of the proximity list. 
Fortunately, such entries represent nodes 
already close-by so the additional cost is kept to a minimum.
However, \emph{PChord} has been reported to exhibit slow convergence speed 
and inefficiency in high-churn environments~\cite{DK2006}.
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% VM:
%% Removed this whole chuck since most of it sounded like
%% repetition of the rest of the text below after all.
%% Please review and remove if you agree.
%%
% Passing through proximity links, in the underlying network, 
% means reduced routing cost. 
% Moreover, if the number of entries in the proximity list is the same
% as the number of network partitions, 
% \emph{PChord} prevents hops from jumping in and
% out of network partitions the current node belongs to.
% On one hand, 
% \emph{PChord}’s advantageous  points are that 
% its routing attains fewer overlay hops, 
% it crosses network partition(s) only once by following proximity links
% and it maintains the light-weight maintenance cost of \emph{Chord}.
% On the other, \emph{PChord} exhibits slow convergence speed 
% and inefficiency in high-churn environments~\cite{DK2006}.
% %%AD rephrased what is below as above... 
% % \emph{PChord}’s advantages include the fact 
% % that the main routing optimizations are of
% % less overlay hops, following proximity links and crossing the same network
% % partition only once along a routing path while in the same time keeping Chord's
% % light-weight maintenance cost. 
% % On the other hand, it exhibits slow convergence
% 	% speed and inefficiency in a high churn environment \cite{DK2006}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\emph{PChord} qualitatively behaves as follows:
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Small decrease in needed overlay hops per object publishing but rigid in
% high churn environments.
medium &
% The are heartbeat mechanism for both finger table and proximity list adds a
% burden to the network by default. But the overall overhead is decreased as
% the proximity list becomes longer.
medium &
% Improvement of routing is achieved with more object pointers helping to
% shorten the routing path of object querying. When the distance of query source
% to target is far away both Chord and PChord achieve the average hop number to
% not increase.
medium
\end{tabular}
}
\end{center}

>>>>

\textbf{\emph{Global Soft-State}} \cite{XTZ2003} builds a global view to help nodes
choose shorter routing paths. To generate the proximity information, it 
combines the landmark binning method with small
scale distance probes to reveal the properties 
of the underlying network. 
%Figure \ref{fig:global_softstate} presents the landmark
%space and the mapping of the position of the nodes.

@@

\begin{tabular}{rccc}
\multicolumn{1}{r}{} &
\multicolumn{1}{c}{\emph{Efficiency}} &
\multicolumn{1}{c}{\emph{Overhead}} &
\multicolumn{1}{c}{\emph{Scalability}}
\\
\cline{2-4}
\emph{Global Soft-State} &

@@

\textbf{\emph{Mithos}}~\cite{WR2003} ensures that neighboring nodes in the overlay are
close also in terms of the underlying layer by integrating proximity layout
and proximity routing overlay optimizations.

@@

A noted Mithos limitation is that the protocol cannot effectively
handle dynamic arrivals and departures from the network~\cite{RGJZ2004}. 
\cite{CCRK2004}~points out extensive probing for Mithos to determine 
distances and less accurate proximity results compared to other
virtual coordinate systems. The last issue  has been also attributed
by~\cite{WSS2005} to the iterative neighbor selection process that is 
reportedly prone to premature termination at local minima.
%%
\cite{cox_vivaldi_2004} argues that elements of the protocol's
synthetic ID generation require a centralized implementation 
affecting Mithos' scalability.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In regard to the three criteria, \emph{Mithos} stands as follows:
\begin{center}
{\footnotesize
\begin{tabular}{rccc}
\multicolumn{1}{r}{} &
\multicolumn{1}{c}{\emph{Efficiency}} &
\multicolumn{1}{c}{\emph{Overhead}} &
\multicolumn{1}{c}{\emph{Scalability}}
\\
\cline{2-4}
\emph{Mithos} &
% It has very good results in reducing communication latency among peers but its
% efficiency is being constrained by the fact that the proximity is calculated
% at bootstrap, assigning virtual coordinates that are used throughout of a
% nodes life cycle and thus the overlay is not adapting to a high-churn
% environment.
medium &
% Incremental probing is applied in quadrants and in two-hop distance at each
% step that does not generate a lot o control overhead.
medium &
% It is constrained by the fact that the protocol does not respond to dynamic
% peer arrivals and departures
low
\end{tabular}
}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{LAPTOP}
%
%%AD what is the nature of the "structure" overlay here???
%% VM the structure is that it is organized as a tree hierarchy.
\textbf{\emph{LAPTOP}}~\cite{WLH2007} organizes the overlay 
into a tree-based hierarchy so that 
hops required during message routing are reduced and 
maintenance overhead is minimized.
A caching scheme is also used 
to further reduce routing table update costs. 
It is theoretically shown that 
\emph{LAPTOP} routing path length is bounded by $O(log_d(N))$ and node
joining and leaving in the overlay network is bounded by
$O(d*log_d(N))$ hops in a balanced overlay tree with $N$ representing the
number of nodes and $d$ the maximum degree of each node (i.e., number of links). 
\emph{LAPTOP} adopts the geographical layout approach  
and constructs its layout in a self-organizing and 
efficient fashion. 
The physical distances are estimated
with round-trip times to a few existing nodes in the overlay network.
%%
Each node is assigned a dot-formatted address (e.g., 1.3.4) with
each octet ranging from $1$ to $d$.
The assignment process is done by appending a unique octet 
to the address of the parent of each node, while
the root node is assigned address $1$.

@@

\begin{tabular}{rccc}
\multicolumn{1}{r}{} &
\multicolumn{1}{c}{\emph{Efficiency}} &
\multicolumn{1}{c}{\emph{Overhead}} &
\multicolumn{1}{c}{\emph{Scalability}}
\\
\cline{2-4}
\emph{LAPTOP} &

@@

To optimize the underlying network use,
\textbf{\cite{KLKP2008}} introduces proximity
controls over the \emph{vanilla Kademlia}~\cite{maymounkov_kademlia_2002} 
protocol's random \emph{ID} assignment.
% The work in this paper
% can also be considered as a more generic study of incorporating proximity into
% iterative lookup algorithms.
In its quest to improve routing performance, the overlay uses 
a cost ``yardstick'' (i.e., metric) provided by the underlying network.
% The overlay tier improves its routing performance using a cost--metric that is
% provided by the underlying tier. 
Such cost information can be acquired by:
\begin{inparaenum}[\itshape i\upshape)]
  \item measuring previous lookups,
  \item exchanging or jointly-computing measurements with others, or 
  \item using a local database to look--up information.
\end{inparaenum}

@@

\emph{Kademlia} proximity injection improves 
locality of connections among peers.
To enhance traffic locality, the use of 
\emph{MaxMind GeoIP} database\footnote{\url{http://www.maxmind.com}} 
is suggested to form clusters of nearby peers.
To this end, Vivaldi coordinates~\cite{cox_vivaldi_2004} could be 
also used as an alternative for morphing locality. 
\cite{KLKP2008} however suggests that the clustering approach 
when combined with \emph{PRS}/\emph{PNS} helps contain 
$40\%$ of messages within an \emph{ISP} and allows only $6\%$ 
to go through the backbone.
The behavior of \cite{KLKP2008} with respect to the stated criteria is deemed as follows:
%%
\begin{center}
{\footnotesize
\begin{tabular}{rccc}
\multicolumn{1}{r}{} &
\multicolumn{1}{c}{\emph{Efficiency}} &
\multicolumn{1}{c}{\emph{Overhead}} &
\multicolumn{1}{c}{\emph{Scalability}}
\\
\cline{2-4}
\emph{\cite{KLKP2008}} &
% Uses static information to cluster nodes which is not the most efficient
% approach in dynamic systems
% PNS reduces lookup latencies by 66\% compared to POK
medium &
% 
medium &
% MaxMind is commercial and cannot be used by FOSS P2P systems. Trying to
% expose information from P2P client can result in security issues.
medium
\end{tabular}
}
\end{center}

@@

\textbf{\emph{CHOP6}} \cite{MT2007} is a Chord-variant DHT that exploits
\emph{IPv6} address format as well as available \emph{RTT} information to 
enable proximity estimation among peers during message routing.
%%
Similar to \emph{Chord}~\cite{stoica_chord_2001}, 
\emph{CHOP6} uses a finger table with each entry now holding $k$$>$$1$ candidate
nodes. 
The next hop for a message is selected to be the one closest to the
destination among those $k$ candidate peers. 
This proximity is determined either
by exploiting RTT measurements or, if there is no such information yet 
(i.e., a new peer appears), by
estimating the distance in the overlay's ID space.

When joining the network, each node
receives a $64$-bit \emph{ID}. 
It comprises of a random part and the IPv6 prefix which 
is obtained by hashing the node's IP address and port
number; this combination is deployed in an effort  
to preserve the uniformity of node assignment. 
The prefix in question is based on IPv6's global routing prefix.
As IANA\footnote{\url{http://www.iana.org/}}  
assigns address blocks to regions (RIRs) which are further
distributed at national level (NIRs), the first $32$-bits of the address
can estimate the region or the country in which the node is connected. 
Thus, CHOP6's IPv6 prefix ID is used for proximity estimation
if no RTT information is available during routing. 
%%
%
%\paragraph{}
% There are three cases in which a node chooses the next hop according to
% information it possesses.
%\begin{itemize}
% \item When no information about RTT is available candidate next hops, the
%  sender just selects a node in the finger table entry which shares the longest
% prefix with the destination.
% \item There is another possibility that after some communication with other
%  nodes, the source node should know of the RTTs to some of the nodes in finger
% table entry. In this case, the source node chooses the one with the smallest
% RTT with probability $p$. If there is a node with no measured RTT then the
% sender can select such a node with probability $1 - p$
% \item In this last case the source node has already communicated with all
%  candidate node in the finger table entry. Thus, the node selects the node
% whose RTT is the smallest with probability $p$, the one with the second
% smallest with probability $q$ and so on, where $0 \leq \ldots < r < q < p < 1$
% and $p+q+r+\ldots \leq 1$
%\end{itemize}
%
With respect to the three qualitative criteria, \emph{CHOP6} stands as follows:
\begin{center}
{\footnotesize
\begin{tabular}{rccc}
\multicolumn{1}{r}{} &
\multicolumn{1}{c}{\emph{Efficiency}} &
\multicolumn{1}{c}{\emph{Overhead}} &
\multicolumn{1}{c}{\emph{Scalability}}
\\
\cline{2-4}
\emph{CHOP6} &
% Simple approach that exploits proximity but it is coarse grained and thus not
% efficient.
low &
% Its static nature imposes low overhead to the network
low &
% IPv6 is still not widely applied and supported.
medium
\end{tabular}
}
\end{center}

@@

%%AD a better connection with the mismatch problem has to be made... 
%%		.. in the form of 1-2 lines (or short statements). 
%%
%% VM Added some extra lines and restructured the text
\textbf{\emph{T2MC}}'s~\cite{SLCGZ2008} objective is to diminish the redundant multiple
messages that may unnecessarily cross autonomous system (\emph{AS}) boundaries.
Inter-\emph{AS} links are the costliest to ISPs and hence, 
minimizing topology mismatches greatly affects pertinent operational expenditure.
%%
To achieve this, each node exploits the stable structure of
the Internet routers to help solve a clustering problem. 
The algorithm uses \emph{traceroute}-logs to detect inter-\emph{AS} boundaries 
and clusters peers to either nearby or 
far-away groups by applying a customized $k$-mean classification ($k=2$).
%%
When joining the network, the peer randomly picks an IP and uses
traceroute and selects the routers with
minimum and maximum latencies in the above \emph{traceroute} path 
as initial centroids for the ``nearby'' and ``far-away'' sets respectively.
Following an iterative procedure, the node comes up with the two sets 
demonstrating minimum intra-set latency variance.
At this stage, routers in the ``far-away'' set are not considered critical.
%%
%%AD skipping the details???? JUST CHECK
% Skipping the details of the algorithm, it picks the routers with
% minimum and maximum latencies in the above traceroute path as initial centroids
% for the ``near'' and ``remote'' sets respectively and after some iterations it
% ends up with two sets having the minimum intra-set latency variance. 
%%
% The router from the ``far-away'' set that presents the closest distance 
% from the peer in terms of hops, is designated as beacon.
% Any node portraying distance longer that the above is classified 
% as 
% 
% to the peer, in terms of hops, is designated as a beacon.
% Any node whose distance is measured to be longer that the distance 
% between 
% 
% The router with the minimum hops in the ``remote'' set is set up as the hop
% threshold and anything above that is classified as the ``remote'' router cluster
% for that peer. 
% Similarly, 
In contrast, the router from the ``near'' set
having the maximum number of hops 
from the just-joining peer is key as it denotes an edge--gateway. 
Peers that share the same edge--gateway or other members in the ``nearby'' 
router cluster are considered intra-\emph{AS} neighbors.
%%AD the final phrase for this is missing! So what??? What is achieved? 1 sentence.

Even though \emph{traceroute}
provides detailed information about the network structure, 
its extensive use may create overhead on the overall network structure. 
Administrators thus frequently
disable \emph{traceroute} support on their routers and this 
undoubtly affects \emph{T2MC}'s operation.
%%
Although overall experimental results have been encouraging, 
\emph{T2MC} is considered rather coarse-grained as it only
classifies neighbors into two groups \cite{QLZG2009}.
%
%T2MC \cite{SLCGZ2008} uses trace-route logs to detect different autonomous
%systems and cluster close by peers, thus reducing redundant traffic that crosses
%autonomous system boundaries. T2MC uses a customized k-mean classification
%algorithm with $k=2$ to perform the classification, and exploits the stable
%structure of the Internet routers to guide clustering. The peer chooses the
%minimum and maximum Latency results from the trace-route to initialize the
%centroids of two sets. Then the peer calculates, for all hops along its
%trace-routed path, the peer calculates the absolute distance to these centroids
%of both sets and assigns the routers to that centroid with which it has the
%smaller absolute distance. After that, the mean and variance values are
%calculated and if the variance is larger than a predefined threshold then the
%algorithm sets the two latency mean values as new centroids for the two sets and
%loops again. Ultimately peer will end up with two sets having the minimum
%intra-set variance. The peer, then, chooses the router from the second set with
%the minimum hops attribute and sets it as a threshold. The selected router and
%all others whose hops attribute is larger than the threshold are classified as
%\emph{remote} router cluster. The remaining are classified as \emph{near}. From
%the near class, the peer chooses the one with maximum hops attribute as its edge
%router, and registers it along with all near clusters into the DHT of the
%\p\ overlay. As new peers join the network, those that share the same edge
%router or any of the members of the near router clusters, would form a close
%peer cluster. As Edge routers can provide more valuable information than other
%members of the near set, T2MC was designed to prioritize interaction of peers
%and edge gateways.
%
%
% TODO: SOME DISCUSSION
%
%The use of Trace-route as a tool for implementing the distance measuring
%infrastructure raise concerns about its efficiency and scalability. Being,
%primarily, a network diagnostic utility,
% Even though trace-route provides detailed information about the network
% structure, its excessive use creates additional overhead that stresses further
% the overall network infrastructure. This forces network administrators to
% disable its support from the routers they manage, thus jeopardizing the
% effectiveness of the T2MC algorithm.
%
\emph{T2MC} fares as follows:
%%
\begin{center}
{\footnotesize
\begin{tabular}{rccc}
\multicolumn{1}{r}{} &
\multicolumn{1}{c}{\emph{Efficiency}} &
\multicolumn{1}{c}{\emph{Overhead}} &
\multicolumn{1}{c}{\emph{Scalability}}
\\
\cline{2-4}
\emph{T2MC} &
% The efficiency of choosing close by peers is very good and reported almost
% 65\% better than that of GNP (and thus generally of static landmarking as a
% whole)
high &
% trace-route is a very heavy tool and thus incurs excessive burden to the
% network resources.
high &
% Trace-route is categorized as too heavy-weighted and intrusive for use in a
% larger scale system \cite{RKHS2002}. Additionally, disabling
% ICMP is a common administrative policy for edge sites to enforce security,
% while dumping BGP routing tables\cite{krishnamurthy_bgpclust_2000} is not
% directly available to the application layer.
low
\end{tabular}
}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{PChord}
\textbf{\emph{PChord}} \cite{HLYW2005} is based on the \emph{Chord DHT} and incorporates
proximity in its routing mechanism. 
To achieve this, the standard finger table
is augmented with a \emph{proximity list} that contains
nodes in the network found nearby in terms of RTT.
%in this way, the next hop can be decided based on both progress
%towards the key and the physical proximity of the candidate nodes.
%%AD
%% I am not sure about the "best progress" term - what does it really mean???
%% VM changed the above slightly to address the above comment. Generally
%% in DHTs when a node receives a search query for a key that it does not have
%% the data for, it routes the request to that node in its routing table that
%% is closest to the key. That is what I mean with best progress to the keys
%% In topology aware systems and topology aware routing we have the requirement
%% that the next hop should be the closest one which in many cases can be
%% a competing requirement with the best progress to the key requirement I
%% just described. 
In this respect, the next hop during routing can be decided based on both the
direction towards the search key and minimizing the cost of that hop.

@@

Unfortunately the overlay maintenance cost is somewhat higher than
\emph{Chord} as additional heart-beat messages are required for
connection verification for the entries of the proximity list. 
Fortunately, such entries represent nodes 
already close-by so the additional cost is kept to a minimum.
However, \emph{PChord} has been reported to exhibit slow convergence speed 
and inefficiency in high-churn environments~\cite{DK2006}.
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% VM:
%% Removed this whole chuck since most of it sounded like
%% repetition of the rest of the text below after all.
%% Please review and remove if you agree.
%%
% Passing through proximity links, in the underlying network, 
% means reduced routing cost. 
% Moreover, if the number of entries in the proximity list is the same
% as the number of network partitions, 
% \emph{PChord} prevents hops from jumping in and
% out of network partitions the current node belongs to.
% On one hand, 
% \emph{PChord}’s advantageous  points are that 
% its routing attains fewer overlay hops, 
% it crosses network partition(s) only once by following proximity links
% and it maintains the light-weight maintenance cost of \emph{Chord}.
% On the other, \emph{PChord} exhibits slow convergence speed 
% and inefficiency in high-churn environments~\cite{DK2006}.
% %%AD rephrased what is below as above... 
% % \emph{PChord}’s advantages include the fact 
% % that the main routing optimizations are of
% % less overlay hops, following proximity links and crossing the same network
% % partition only once along a routing path while in the same time keeping Chord's
% % light-weight maintenance cost. 
% % On the other hand, it exhibits slow convergence
% 	% speed and inefficiency in a high churn environment \cite{DK2006}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\emph{PChord} qualitatively behaves as follows:
\begin{center}
{\footnotesize
\begin{tabular}{rccc}
\multicolumn{1}{r}{} &
\multicolumn{1}{c}{\emph{Efficiency}} &
\multicolumn{1}{c}{\emph{Overhead}} &
\multicolumn{1}{c}{\emph{Scalability}}
\\
\cline{2-4}
\emph{PChord} &
% Small decrease in needed overlay hops per object publishing but rigid in
% high churn environments.
medium &
% The are heartbeat mechanism for both finger table and proximity list adds a
% burden to the network by default. But the overall overhead is decreased as
% the proximity list becomes longer.
medium &
% Improvement of routing is achieved with more object pointers helping to
% shorten the routing path of object querying. When the distance of query source
% to target is far away both Chord and PChord achieve the average hop number to
% not increase.
medium
\end{tabular}
}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{AChord}
\textbf{\emph{AChord}} \cite{DK2006} exploits IPv6's \emph{anycast} mechanism to
relieve the protocol from complex joining procedures,
harness network proximity and achieve high routing efficiency. 
When sending a message to an IPv6 anycast group, 
the originator accomplishes this delivery by interacting with
the physically closest node in that group~\cite{M2002}.
Thus, \emph{AChord} organizes all nodes participating
in the overlay network into a single anycast group. 
An arriving peer is automatically forwarded to the physically 
nearest node for
bootstrapping; this curtails the need to explicitly maintain participants
and the effort of locating the physically nearest. 
%%
